Make manuscript figures

### 2022-06-13 scripts/R/make_manuscript_figures.rmd
fix labels on tip trait cor figure

ggplot(data = tip_pair_data_corelations, aes(x = factor(dist_decile_rank), y = correlation)) +
        geom_boxplot() + 
        facet_grid(alpha ~ H2, labeller = plot_labeller) + 
        labs(x = "Tree distance decile", y = "Pearson correlation in trait value") + 
        shared_theme
ggsave(filename = "figures/tip_trait_correlation.png", width = linewidth, height = height, unit = "cm")

>>>>

tip_pair_data_to_plot <- tip_pair_data_corelations %>%
        rename("Selection strength" = alpha) %>%
        mutate(Heritability = factor(H2, levels = c(0.75, 0.15)))

ggplot(data = tip_pair_data_to_plot, aes(x = factor(dist_decile_rank), y = correlation)) +
        geom_boxplot() + 
        facet_grid(Heritability ~ `Selection strength`, labeller = label_both) + 
        labs(x = "Tree distance decile", y = "Pearson correlation in trait value") + 
        shared_theme
ggsave(filename = "figures/tip_trait_correlation.png", width = linewidth, height = height * 2/3, unit = "cm")
